---
title: "Testing the CATs"
author: "George"
date: `r Sys.Date()`
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(mirtCAT)

preferred_design = list(min_items = 25,
                        max_items = 50, 
                        min_SEM = 0.15) 

set.seed(123) 
# Note: despite doing this, generate_pattern creates random response patterns each time
```

## English Production 

```{r english, echo=F}
load("app/API/eng_ws_wg_mod_2pl_nobad.Rds")

pattern0 <- generate_pattern(mod_2pl, Theta = 0) # sum(pattern0) = 161
pattern1 <- generate_pattern(mod_2pl, Theta = 1) # sum(pattern1) = 456

choices <- matrix(c(0,1), nrow(coefs_2pl), 2, byrow = TRUE)
questions <- coefs_2pl$definition
df <- data.frame(Question=questions, 
                 Option = choices, 
                 Type = 'radio', stringsAsFactors = FALSE)

# start_item = 'MI',
# index 35 = ball (start item for 13-17 mos)
res0 <- mirtCAT(df, mod_2pl, local_pattern=pattern0, criteria = 'MI', start_item = 35, method = 'ML', 
               design = preferred_design) 

# index 326 = leg (25-month-old)
res1 <- mirtCAT(df, mod_2pl, local_pattern=pattern1, criteria = 'MI', start_item = 326, method = 'ML', 
               design = preferred_design) 

seq0 = tibble(item = coefs_2pl[res0$items_answered,]$definition,
         response = res0$scored_responses[res0$items_answered],
         theta = res0$thetas_history[-1])

seq1 = tibble(item = coefs_2pl[res1$items_answered,]$definition,
         response = res1$scored_responses[res1$items_answered],
         theta = res1$thetas_history[-1])

#write.csv(seq0, file="test_sequences/en_CAT_test_theta0_ball.csv", row.names = F) # Theta_1 = .09 SE=.099 (29 items)
#write.csv(seq1, file="test_sequences/en_CAT_test_theta1_leg.csv", row.names = F) # Theta_1 = .84 SE=.094 (25 items)
```

We show example CATs for two simulated participants, one with ability (theta) = 0, and one with theta = 1. The CAT asks a minimum of 25 items, terminates when the SEM=0.15, or when 50 items is reached.
The theta=0 participant (left) answered `r length(res0$items_answered)` questions, and the theta=1 participant (right) answered `r length(res1$items_answered)`. 
The final estimated theta for the theta=0 participant was `r round(as.vector(res0$thetas),3)`, and for the theta=1 participant was `r round(as.vector(res1$thetas),3)`. 

## Spanish Production


```{r spanish, echo=FALSE}
# load spanish model
load("app/API/sp_ws_wg_mod_2pl_nobad.Rds")

# generate response patterns
pattern0 <- generate_pattern(mod_2pl, Theta = 0)
pattern1 <- generate_pattern(mod_2pl, Theta = 1)

choices <- matrix(c(0,1), nrow(coefs_2pl), 2, byrow = TRUE)
questions <- coefs_2pl$definition
df <- data.frame(Question=questions, 
                 Option = choices, 
                 Type = 'radio', stringsAsFactors = FALSE)

# 'agua' start item (ages 12-17)
res0 <- mirtCAT(df, mod_2pl, local_pattern=pattern0, criteria = 'MI', start_item = 21, method = 'ML', 
               design = preferred_design) 
# 'cama' start item (ages 22-24)
res1 <- mirtCAT(df, mod_2pl, local_pattern=pattern1, criteria = 'MI', start_item = 125, method = 'ML', 
               design = preferred_design) 


seq0 = tibble(item = coefs_2pl[res0$items_answered,]$definition,
         response = res0$scored_responses[res0$items_answered],
         theta = res0$thetas_history[-1])

seq1 = tibble(item = coefs_2pl[res1$items_answered,]$definition,
         response = res1$scored_responses[res1$items_answered],
         theta = res1$thetas_history[-1])

#write.csv(seq0, file="test_sequences/sp_CAT_test_theta0_agua.csv", row.names = F) # Theta_1 = -.19 SE=.108 (25 items)
#write.csv(seq1, file="test_sequences/sp_CAT_test_theta1_cama.csv", row.names = F) # Theta_1 = .98 SE=.11 (25 items)
```

We show example CATs for two simulated participants, one with ability (theta) = 0, and one with theta = 1. The CAT asks a minimum of 25 items, terminates when the SEM=0.15, or when 50 items is reached.
The theta=0 participant (left) answered `r length(res0$items_answered)` questions, and the theta=1 participant (right) answered `r length(res1$items_answered)`. 
The final estimated theta for the theta=0 participant was `r round(as.vector(res0$thetas),3)`, and for the theta=1 participant was `r round(as.vector(res1$thetas),3)`. 


## French Production


```{r french, echo=FALSE}
# load french model
load("app/API/fr_ws_wg_mod_2pl_nobad.Rds")

# generate response patterns
pattern0 <- generate_pattern(mod_2pl, Theta = 0)
pattern1 <- generate_pattern(mod_2pl, Theta = 1)

choices <- matrix(c(0,1), nrow(coefs_2pl), 2, byrow = TRUE)
questions <- coefs_2pl$definition
df <- data.frame(Question=questions, 
                 Option = choices, 
                 Type = 'radio', stringsAsFactors = FALSE)

# index 16 = au.revoir (start item for 12-14 mos)
res0 <- mirtCAT(df, mod_2pl, local_pattern=pattern0, criteria = 'MI', start_item = 16, method = 'ML', 
               design = preferred_design) 

# index 148 = couche (vêtements) (start item for 24 mos)
res1 <- mirtCAT(df, mod_2pl, local_pattern=pattern1, criteria = 'MI', start_item = 148, method = 'ML', 
               design = preferred_design) 

seq0 = tibble(item = coefs_2pl[res0$items_answered,]$definition,
         response = res0$scored_responses[res0$items_answered],
         theta = res0$thetas_history[-1])

seq1 = tibble(item = coefs_2pl[res1$items_answered,]$definition,
         response = res1$scored_responses[res1$items_answered],
         theta = res1$thetas_history[-1])

write.csv(seq0, file="test_sequences/fr_CAT_test_theta0_12mos.csv", row.names = F) # Theta_1 = .022 (25 items)
write.csv(seq1, file="test_sequences/fr_CAT_test_theta1_24mos.csv", row.names = F) # Theta_1 = 1.11 (40 items)
```

## Japanese Production

```{r japanese, echo=FALSE}
# load french model
load("app/API/jp_ws_wg_mod_2pl_prior.Rds")

# generate response patterns
pattern0 <- generate_pattern(mod_2pl, Theta = 0)
pattern1 <- generate_pattern(mod_2pl, Theta = 1)

choices <- matrix(c(0,1), nrow(coefs_2pl), 2, byrow = TRUE)
questions <- coefs_2pl$definition
df <- data.frame(Question=questions, 
                 Option = choices, 
                 Type = 'radio', stringsAsFactors = FALSE)

# index 245 = (イナイイナイ) バー (start item for 12-13 mos)
res0 <- mirtCAT(df, mod_2pl, local_pattern=pattern0, criteria = 'MI', start_item = 245, method = 'ML', 
               design = preferred_design) 

# index 115 = 足 (あし) (start item for 24-25 mos)
res1 <- mirtCAT(df, mod_2pl, local_pattern=pattern1, criteria = 'MI', start_item = 115, method = 'ML', 
               design = preferred_design) 

seq0 = tibble(item = coefs_2pl[res0$items_answered,]$definition,
         response = res0$scored_responses[res0$items_answered],
         theta = res0$thetas_history[-1])

seq1 = tibble(item = coefs_2pl[res1$items_answered,]$definition,
         response = res1$scored_responses[res1$items_answered],
         theta = res1$thetas_history[-1])

write.csv(seq0, file="test_sequences/jp_CAT_test_theta0_12mos.csv", row.names = F) # Theta_1 = .051 (25 items)
write.csv(seq1, file="test_sequences/jp_CAT_test_theta1_24mos.csv", row.names = F) # Theta_1 = 1.07 (25 items)
```
